# Results 

```{r prepare cluster evaluation plot, echo = F, warning = FALSE, message = FALSE}
source("doc/scripts/prepare_cluster_evaluation.R")
```

```{r results prepare indval}
source("doc/scripts/results_indval.R")
```

```{r results prepare TA}
source("doc/scripts/results_ta.R")
```

```{r}
cmn_t_1 = paste(round(cmn_a_1/n_sites,3)*100, "%")
cmn_t_2 = paste(round(cmn_a_2/n_sites,3)*100, "%")
cmn_t_3 = paste(round(cmn_a_3/n_sites,3)*100, "%")
cmn_t_4 = paste(round(cmn_a_4/n_sites,3)*100, "%")
cmn_t_5 = paste(round(cmn_a_5/n_sites,3)*100, "%")
```

## Comparison of classifications 
<!-- Overview over results --> 
Overall Illies received the highest score, with `r rank_dat[typ == "illies", total_points]` of 20 possible points, followed by BGR (`r rank_dat[typ == "eea", total_points]`), BRT12 (`r rank_dat[typ == "brt12", total_points]`), GloRiC (`r rank_dat[typ == "gloric", total_points]`) and BRT20 (`r rank_dat[typ == "brt20", total_points]`). 

<!-- CH -->
The CH was higher in regional typologies than in reach-based typologies and higher in in BGR than in Illies' ecoregions. 
BRT12 had a higher score than BRT20 and GloRiC had the lowest CH. 

<!-- classification strength --> 
Most typologies had similar CS, approximately `r cs_eea`.
Only Illies' ecoregions exceeded 0.05 with a score of `r cs_ill`.     

<!-- IndVal Scores -->
The Illies' ecoregions had the largest IVS closely followed by GloRiC.
These two were very close to the biological classification.
The three other typologies had similar IVS around `r iv_brt20`. 
        
<!-- ASW -->
Increasing the emphasis on compactness (i.e. $p$) decreased the silhouette widths (Figure \@ref(fig:fig-res-sw)).
All typologies had positive $ASW_{min}$, BGR and Illies' ecoregions were close to the biological typology.
Reach-based typologies had lower $ASW_{min}$ than regional ones and GloRiCs was slightly higher than the similar scores of BRT12 and BRT20. 
With $p = 1$, only the ASW of BGR exceeded zero and the random typology. 
In the remaining typologies, the difference between region- and reach-based typologies shrunk.
Illies' ecoregions had a slightly higher ASW than BRT12, which had a higher ASW than BRT20.
GloRiC had the lowest ASW.
The $ASW_{max}$ is negative for all typologies, including the biological. 
The absolute value only declined markeldy for BGR, Ilies ecoregions and GloRiC, so that BRT12 had the highest $ASW_{max}$. 
It was followed by BGR, BRT12, Illies' ecoregions and GloRiC. 


```{r fig-res-sw, fig.align="center", fig.height=5, fig.cap="Cluster validity citeria for freshwater typologies. (a) Calinski Harabasz, Classification Strength and Indicator Value score of all eight freshwater typologies. (b) Generalized Silhouette width over the degrees p of the mean. The dashed horizontal line indicates a score of zero."}
img <- readPNG("figures/eval_cluster_combined.png")
grid.raster(img)
```



## Typical assemblages

We combined the most types in .... 

How many taxa in which TA ... 

Size differenes .... 

Viusalizaton ... see miro board. 

How many in % 


We combined the broad river types BRT4 and 5, BRT 2, 3, 8, 9, 10, 11 and 18 as well as BRT 15 and 16 because their Jaccard similarity exceeded 0.8. 
The BRT4_5 type represents lowland, calcareous rivers irrespective of size, BRT2_3_8_9_10_11 represents low and mid-altitude rivers of varying geology and BRT 15_16 represents non-siliceous high-altitude rivers. 


`r ta_used_taxa` of `r ta_total_taxa` taxa were included in the typical assemblages.
Most at the `r ta_mostcommon_lvl` level (`r ta_mostcommon_lvl_n`), followed by `r ta_secondcommon_lvl` (`r ta_secondcommon_lvl_n`) and `r ta_leastcommon_lvl` (`r ta_leastcommon_lvl_n`). 
On average, taxa occurred in `r ta_mu_occ` typical assemblages. 
The family Chironomidae was included in all typical assemblages.
The most common genera were Ancylus, Baetis, Esolus, Hydropsyche, and Limnius all of which occurred in four typical assemblages.
*Serratella ignita* was the only species included in the typical assemblages and was typical for BRT4_5, BRT2_3_8_9_10_11 and BRT15_16.
The average size of typical assemblages was `r ta_mean_size` with a standard deviation of `r ta_sd_size`.
The largest typical assemblage was `r ta_biggest_name` with `r ta_biggest_size` taxa and the smallest was `r ta_smallest_name` with `r ta_smallest_size` taxa. 
To compare taxonomic resolution across typical assemblages, we assigned a value of three to each species, two to genera and one to lower taxonomic levels. 
The mean taxonomic resolution was `r round(ald_overall$mean2,1)` with a standard deviation of `r round(ald_overall$sd,1)`.
The river type BRT4_5  had the highest taxonomic resolutions (2). 
BRT14 and BRT18 had the lowest taxonomic resolution (1.0)
